\documentclass[a4paper, 11pt, oneside]{report}
\usepackage{tcdthesis}

\usepackage[utf8]{inputenc}
\usepackage{csquotes}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{booktabs}
\usepackage{float}
\usepackage{tabularx}
\usepackage{import}
\usepackage{apacite}
\usepackage{natbib}
\usepackage{url}
\usepackage{tikz}
\usepackage[acronym]{glossaries}
\usepackage{enumitem}
\usepackage{textcomp}
\usepackage{eurosym}
\usepackage[printonlyused]{acronym}
\usepackage{amssymb}
\usepackage{pifont}
\usepackage{amsmath}
\usepackage{times}
\usepackage{textcomp}
\usepackage{pgfplots}
\usepackage{array}
\usepackage{csvsimple}
\usepackage{hyperref}

\newcolumntype{M}[1]{>{\centering\arraybackslash}m{#1}}
\newcolumntype{N}{@{}m{0pt}@{}}

\usepackage {fancyhdr}
\fancyhf{}
\setlength{\headheight}{15pt}
\rhead{\thepage}
\lhead{\textit{\nouppercase{\leftmark}}}

\newcommand{\xmark}{\ding{55}}%
\newcommand{\cmark}{\ding{51}}%

\mastersthesis
\oneandhalfspace
\leftchapter

\renewcommand{\thesisauthor}{Wesley Fung}
\renewcommand{\thesismonth}{May}
\renewcommand{\thesisyear}{2017}
\renewcommand{\thesistitle}{VANET: Evaluating Smart Parking Performance in a Dublin Scenario}
\renewcommand{\thesisauthorpreviousdegrees}{}
\renewcommand{\thesissupervisor}{Siobhán Clarke}
\renewcommand{\thesisauthoraddress}{...}
\renewcommand{\thesisdedication}{}

\begin{document}

\thesistitlepage
\thesisdeclarationpage

\begin{thesissummary}
\import{}{./Summary/0_problem.tex}
\import{}{./Summary/1_related.tex}
\import{}{./Summary/2_solution.tex}
\import{}{./Summary/3_results.tex}
\end{thesissummary}

\begin{thesisabstract}
    Traffic congestions and pollution is a major issue in many cities worldwide. Drivers cruising for parking spaces contribute heavily to these issues. For this reason, many researchers have performed studies on the topic of smart parking, as well as \ac{VANET}. With the introduction of smart parking, drivers can know where vacant parking spaces are. However, as an argument proposed by this dissertation, the surfacing of parking space information is not enough. Simply by knowing a parking spot is vacant does not guarantee any driver a parking spot. A solution must be found to minimise the chances of a driver arriving at a parking spot that became occupied minutes beforehand.
    
    \ac{VANET} is a technology that supports inter-vehicular communications. \ac{VANET} technologies allow vehicles to communicate with other vehicles to ensure driver safety. As well as this, vehicles may relay information to \ac{RSU} for traffic light coordinate as well as traffic queue management. This work is concerned with the integration of a smart parking system supported by \ac{VANET}.
    
    Dublin City is the domain of interest in this dissertation. For this reason, Dublin City-specific data is acquired from various sources. The data is used in the simulation to build a realistic view on the current parking behaviours of Dublin City. This work is concerned with using a simulation software to build a \ac{VANET} smart parking system evaluated on Dublin City. Vehicles communicate with each other regarding parking space occupancies and vacancies. This involves the integration of Dublin specific traffic and parking data into the simulation.
    
    The evaluation process involves comparing a baseline model to the \ac{VANET} model as described above. The evaluation results show that \ac{VANET} smart parking model minimises the amount of emissions produced. As well as this, a \ac{VANET} smart parking model minimises the chances of drivers arriving at parking spots that are occupied minutes beforehand.
\end{thesisabstract}

\begin{thesisacknowledgments}
I would like to thank the following people for their continuous support, patience and time throughout the course.
\begin{itemize}
    \setlength\itemsep{0em}
    \item My academic supervisor Prof. Siobhán Clarke for her knowledge, expertise and help throughout the year.
    \item My family for their continued support throughout my entire college career.
    \item My classmates in Integrated Computer Science for their continuous motivation.
    \item Dublin City Council staff for providing the required traffic data.
    \item ParkingTag staff for providing the required parking data.
    \item Dr. Christopher Sommer of VEINS for assisting me on questions I had about \ac{VANET} simulation modelling in VEINS.
    \item Simulation of Urban MObility (SUMO) staff for answering my questions regarding SUMO.
\end{itemize}
\end{thesisacknowledgments}

\pagebreak

\tableofcontents                                  %% Generate table of contents.
\listoftables                                     %% Uncomment this to generate list of tables.
\listoffigures                                    %% Uncomment this to generate list of figures.

\pagebreak

%%
%% Acronyms
%%
\chapter*{List of Acronyms}
\addcontentsline {toc}{chapter}{List of Acronyms}
\begin{acronym}
    \acro{ANPR}{Automatic Number Plate Recognition}
    \acro{CNN}{Convolutional Neural Network}
    \acro{DCC}{Dublin City Council}
    \acro{CCTV}{Closed Circuit Television}
    \acro{CLI}{Command Line Interface}
    \acro{EPA}{Environmental Protection Agency}
    \acro{GUI}{Graphical User Interface}
    \acro{HC}{Hybird Cloud}
    \acro{ITS}{Intelligent Traffic System}
    \acro{IVC}{Inter-Vehicle Communication}
    \acro{JOSM}{Java OpenStreetMaps}
    \acro{MANET}{Mobile Ad-Hoc Networking}
    \acro{OBU}{On-Board Unit}
    \acro{OMNeT++}{Objective Modular Network Testbed in C++}
    \acro{OSM}{OpenStreetMaps}
    \acro{RFID}{Radio Frequency IDentification}
    \acro{RSU}{Road Side Unit}
    \acro{SUMO}{Simulation of Urban MObility}
    \acro{SVM}{Supported Vector Machines}
    \acro{TSA}{Travelling Salesman Algorithm}
    \acro{VANET}{Vehicular Ad-Hoc Networking}
    \acro{VEINS}{Vehicles in Network Simulation}
    \acro{VCC}{Vehicle Cloud Computing}
    \acro{VC}{Vehicle Cloud}
    \acro{VuC}{Vehicle using Cloud}
    \acro{V2G}{Vehicle-to-Grid}
    \acro{V2I}{Vehicle-to-Infrastructure}
    \acro{V2V}{Vehicle-to-Vehicle}
\end{acronym}

%%
%% Include thesis chapters here...
%%
  \include{./Template/chapter1}
  \include{./Template/chapter2}
  \include{./Template/chapter3}
  \include{./Template/chapter4}
  \include{./Template/chapter5}
  \include{./Template/chapter6}

%\addcontentsline {toc}{chapter}{Bibliography}     %% Force Bibliography to appear in contents

\bibliographystyle{apacite}
\bibliography{./mendeley.bib}

\addcontentsline{toc}{chapter}{Appendices}       %% Force Appendices to appear in contents
\begin{appendix}
    \include{./Template/appendix1}
\end{appendix}

\end{document}