\subsection{Dublin Traffic Flows} \label{ssec:traffic_flows}
Dublin City traffic flow is incorporated into the simulation. The reason for this is to provide a realistic Dublin City traffic model. 

A visit was made to the Dublin City Councils' traffic department in order to obtain this data. In most major junctions in Dublin, ultrasonic sensors are embedded beneath the ground just before the junctions' traffic lights. The sensor is able to detect whether a vehicle is above it. The sensor also acts as a counter, thus recording the amount of traffic that passes a particular lane on the road. 

On some roads, there is a secondary sensor embedded into the ground further along the road. If there is a stationary vehicle detected above the secondary sensor, the traffic control station knows that that particular road segment has a traffic queue. At the time of writing, DCC traffic control centre does not have a sophisticated self-optimising traffic queue management system.

The obtained traffic flow data contains hourly intervals of the amount of vehicles that have passed the junctions of interest. The time interval of the data is from January 2016 through to December 2016.

Table \ref{table:trafficflow} lists the roads that Dublin traffic flow data is recorded from, along with their national road identifier. The areas that they originate from are also included.

\begin{table}[H]
    \begin{center}
        \begin{tabular}{||c c c||} 
            \hline
            Road Name & Road ID & Areas Served\\ [0.5ex] 
            \hline\hline
            Amiens Street & R105 & Fairview / Clontarf / Marino\\ 
            \hline
            Constitution Hill & R108 & Phisboro / Glasnevin\\
            \hline
            East Wall Road & R131 & Dublin Port Tunnel / East Wall \\
            \hline
            High Street & R810 & Rialto / Inchicore \\
            \hline
            Mount Street Lower & R118 & Ballsbridge \\
            \hline
            Parnell Square East & N/A & Drumcondra / Whitehall \\
            \hline
            Patrick Street & R137 & Harold's Cross \\
            \hline
            Pearse Street & R802 & Ringsend / Irishtown \\
            \hline
            Stephen's Green East & R138 & Donnybrook \\
            \hline
            Victoria Quay & R148 & Chapelizod / Ballyfermot \\
            \hline
            Wexford Street & R114 & Rathmines / Ranelagh \\ [1ex]
            \hline
        \end{tabular}
        \caption{Dublin Traffic Flow Locations}
        \label{table:trafficflow}
    \end{center}
\end{table}