\subsubsection*{Laser Scanners}
Laser range finders are used to detect the distances from a source point into the distance. In a research paper \citep{ono_probe_2002}, a test vehicle with laser range finders attached to the side of the test vehicle makes an attempt to detect on-street parking space occupancies. The laser scanners can retrieve depth information from the side of the test vehicle to the side of the street. With a known location of parking spaces, it would be able to analyse the distance between the test vehicle to the side of the street at a known parking spot location. Thus, it would be able to infer whether or not the parking space is occupied by analysing the distance between the test vehicle and the side of the street. If the distance exceeds the distance between the test vehicle and the kerb, then it's likely that that space is vacant. Whereas if the distance is less than the normal distance between the test vehicle and the kerb, then it is probably taken.

At times, the study found that the detection of black vehicles goes unnoticed. Thus, this paper has devised two algorithms to further enhance the analysis of a normalised depth image obtained from the laser range finder. They are known as the height-curve method and the depth-curve method. The methods include computer vision techniques, such as edge detection to obtain additional information from the depth images. With the depth-curve method, it can find the edge of the road, and if a vehicle is present, it can detect the outline of the vehicle. Using the height-curve method, it can infer whether the height of outline obtained through the depth-curve method is a vehicle or a wall. Through the utilisation of both methods, the study concludes that it provides an accurate solution for the detection of parking space occupancies with a laser range finder.

While the use of laser range finders is possible in the discovery of parking spaces, it requires a vehicle to drive around, scanning all known parking spaces to provide updates. One idea would be to attach these laser range-finders to the side of taxis. Similarly, they could be attached to other forms of public transport systems. However, taxis are expected to cover more ground and circulate more granular areas within an urban environment than general public transport.